---
title: "Module 1 - The R Programming Environment"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

## 1 - Setting up Swirl
This is just a quick guide of how one can submit ones code to coursera.

## 2 - Basic Building Blocks
R can be used as a simple calculator using +, -, * and /
```{r calculator}
5 + 7
```

A simpler method is to define elements as a variable.
```{r define variable}
x <- 5+7
```

You can view a variable by typing its name

```{r}
x
```

Now im storing the variable y as x-3
```{r}
y <- x-3
```

We will now create a vector with the c() function.

```{r}
z <- c(1.1, 9, 3.14)
```

We can view the results of different variables inside other functions

```{r}
c(z, 555, z)
```

We can take the square root of something like this
```{r}
my_sqrt <- sqrt(z - 1)
```

New element called my_div is created, which is the result of z/my_sqrt. In this command R takes the three numbers present in z and divides each of them with the content of my_sqrt. The first number would then be 1.1/3.48, which equals 0.316.
```{r}
my_div <- z/my_sqrt
```

If the number of elements dont match in each group R recycles the shorter vector. We can see an example of this here:
```{r}
c(1, 2, 3, 4) + c(0, 10)
```

If the shorter vector does not divide evenly into the recyceling function the following occurs.
```{r}
c(1, 2, 3, 4) + c(0, 10, 100)
```

## 3 - Sequences of Numbers

